``Interestingness'' in Mathematical Theory Exploration

### 2019-10-22 PhDThesis/bucketing.tex
TODOs
Fixes

\iffalse TODO: Alison: This is very clear and good. Each chapter should have
this at the start \fi
In this chapter we will:

\begin{enumerate}
  \item Define the \emph{signature selection problem} for theory exploration.
  \item Analyse system performance on the Theory Exploration Benchmark, to
    demonstrate the effect of ``toxic'' definitions leading to timeouts.
  \item Analyse the effect of signature selection on the quantity of desirable
    properties attainable by theory exploration on this problem set.
  \item Demonstrate how the signature selection problem is distinct from the
    well-known \emph{clustering problem} in machine learning, and how clustering
    algorithms cannot be directly applied to signature selection.
\end{enumerate}

\iffalse
TODO: Alison: Are you aiming to produce a set of recommendation for TE
researchers to follow here?

My thoughts: Not really. We are identifying an open problem (our attempt at a
solution turns out not to work :( )
\fi

>>>>

In this chapter we will:

\begin{enumerate}
\item Define the \emph{signature selection problem} for theory exploration.
\item Analyse the effect of signature selection on the quantity of desirable
  properties attainable by theory exploration on the Theory Exploration
  Benchmark problem set.
\item Identify the effect of ``toxic'' definitions on system performance, as
  measured by the Theory Exploration Benchmark.
\item Demonstrate how the signature selection problem is distinct from the
  well-known \emph{clustering problem} in machine learning, and how clustering
  algorithms cannot be directly applied to signature selection.
\item Propose recommendations to take signature selection and toxic definitions
  into account.
\end{enumerate}

### 2019-10-22 PhDThesis/litreview_testing.tex
Fixes

\quickcheck{}~\cite{claessen2011quickcheck} popularised the use of
property checking in Haskell, and has subsequently been ported to many other
programming languages. \quickcheck{} generates input data \emph{randomly},
either using explicit generators (via a function called \hs{forAll}), or by
choosing a default generator for types implementing its \hs{Arbitrary}
typeclass (the recent \texttt{hedgehog} package works in a similar way\iffalse
\cite{TODO} \fi).

>>>>

\quickcheck{}~\cite{claessen2011quickcheck} popularised the use of
property checking in Haskell, and has subsequently been ported to many other
programming languages. \quickcheck{} generates input data \emph{randomly},
either using explicit generators (via a function called \hs{forAll}), or by
choosing a default generator for types implementing its \hs{Arbitrary}
typeclass (the recent \texttt{hedgehog} package works in a similar way).
